\ProvidesFile{phidg_textlcd088.tex}[v1.0.1]
\startPlugin{\pluginNameS{Phidgets}{TextLCD088}}{Phidgets}{TextLCD088}

\pluginItemDescription{\pluginNameD{Phidgets}{TextLCD088} corresponds to the PhidgetTextLCD 20X2 with 0/8/8 InterfaceKit device,
which displays text on an LCD screen with two rows of twenty characters,
as well as providing eight digital inputs and eight digital outputs.}

\pluginItemCreated{December 2003}

\pluginItemVersion{1.0.1}

\pluginItemCommands[]

  \pluginListCmdBegin

  \pluginListCmdItem{standard-do}{flip\textnormal{/}on\textnormal{/}off port}  
  Set the state of the specified digital output port to `1' (`on'), `0' (`off') or the reverse of its current state (`flip').
  The port is limited to between 1 and 8.

  \pluginListCmdItem{standard-do}{to backlight on\textnormal{/}off}
  Turns the LCD screen backlight on or off.

  \pluginListCmdItem{standard-do}{to clear \textnormal{[}1\textnormal{/}2\textnormal{]}}
  Clears the top row of the LCD screen (`1'), the bottom row (`2') or both rows, if no argument is given.

  \pluginListCmdItem{standard-do}{to cursor left\textnormal{/}right}
  Move the cursor of the LCD screen left or right.

  \pluginListCmdItem{standard-do}{to display left\textnormal{/}right}
  Shift the text displayed on the LCD screen either left or right.

  \pluginListCmdItem{standard-do}{to entrymode \textnormal{[}reverse\textnormal{]} \textnormal{[}shift\textnormal{]}}
  Specify the text entry mode of the LCD screen.
  If `reverse' is specified, the text entry position decreases after each character is added to the screen.
  If `reverse' is not specified, the text entry position increases after each character is added to the screen.
  If `shift' is specified, the screen is shifted after each character is added to the screen,
  in the direction opposite to the text entry.
  The entered text appears to stay still while the rest of the screen moves.
  If `shift' is not specified, the screen is not shifted.
  
  \pluginListCmdItem{standard-do}{to go row \textnormal{[}column\textnormal{]}}
  Move the text entry point for the LCD screen to the given row (either `1' or `2') and the given column (between 1 and 20).
  If the argument \objCmdArg{column} is not present, it is assumed to be one.

  \pluginListCmdItem{standard-do}{to off}
  Turn off the LCD screen.

  \pluginListCmdItem{standard-do}{to on \textnormal{[}blink\textnormal{]} \textnormal{[}cursor\textnormal{]}}
  Turn on the LCD screen.
  The cursor format is indicated by the keywords `blink' and `cursor'.
  If `blink' is specified, a block cursor will be used (the whole text cell at the cursor location will blink off and on).
  If `cursor' is specified, an underline cursor will be used.
  Both `blink' and `cursor' can be specified.

  \pluginListCmdItem{standard-do}{trigger on\textnormal{/}off}
  Enables or disables the digital input triggering mechanism.
  If the mechanism is enabled, a change to one of the digital inputs results in the transmission of the current digital
  input through the report output of the \objName{fidget} object.
  The digital input is sent as the list `\pluginCmd{\textitcorr{standard-response}} di value bit$_1$ $\ldots$ bit$_8$'.
  The digital values are limited to between 0 and 255.
  
  \pluginListCmdItem{standard-do}{to write anything}
  Display the given values as text on the LCD screen.

  \pluginListCmdItem{standard-get}{di\textnormal{/}do}  
  Sends the current digital input (`di') or digital output (`do') out the report output of the \objName{fidget} object.
  The digital input is sent as the list `\pluginCmd{\textitcorr{standard-response}} di value bit$_1$ $\ldots$ bit$_8$' and
  the digital output is sent as the list `\pluginCmd{\textitcorr{standard-response}} do value bit$_1$ $\ldots$ bit$_8$'.
  The digital values are limited to between 0 and 255.

  \pluginListCmdItem{standard-put}{bits}  
  Sets the digital output to the given value.
  The argument \objCmdArg{bits} is limited to between 0 and 255.
  Each of the digital output ports is set to the corresponding bit of the value.  

  \pluginListCmdEnd

\pluginItemComments

\pluginEnd{\pluginNameE{Phidgets}{TextLCD088}}

% $Log: phidg_textlcd088.tex,v $
% Revision 1.5  2006/07/20 04:47:53  churchoflambda
% Re-added the files to record their changes.
%
% Revision 1.3  2005/08/02 15:07:09  churchoflambda
% Added CVS tags; add rail diagrams for pfsm, map1d, map2d, map3d and listen.
%
