\ProvidesFile{phidg_interfacekit888.tex}[v1.0.1]
\startPlugin{\pluginNameS{Phidgets}{InterfaceKit888}}{Phidgets}{InterfaceKit888}

\pluginItemDescription{\pluginNameD{Phidgets}{InterfaceKit888} corresponds to the PhidgetInterfaceKit 8/8/8 device,
which has eight analog inputs, eight digital inputs and eight digitial outputs.}

\pluginItemCreated{December 2003}

\pluginItemVersion{1.0.1}

\pluginItemCommands[]
  \pluginListCmdBegin

  \pluginListCmdItem{standard-do}{flip\textnormal{/}on\textnormal{/}off port}
  Set the state of the specified digital output port to `1' (`on'), `0' (`off') or the reverse of its current state (`flip').
  The port is limited to between 1 and 8.
  
  \pluginListCmdItem{standard-do}{trigger on\textnormal{/}off}
  Enables or disables the digital input triggering mechanism.
  If the mechanism is enabled, a change to one of the digital inputs results in the transmission of the current digital
  input through the report output of the \objName{fidget} object.
  The digital input is sent as the list `\pluginCmd{\textitcorr{standard-response}} di value bit$_1$ $\ldots$ bit$_8$'.
  The digital values are limited to between 0 and 255.
  
  \pluginListCmdItem{standard-get}{ai\textnormal{/}di\textnormal{/}do}
  Sends the current analog input (`ai'), digital input (`di') or digital output (`do') out the report output of the \objName{fidget} object.
  The analog input is sent as the list `\pluginCmd{\textitcorr{standard-response}} ai analog$_1$ $\ldots$ analog$_8$',
  the digital input is sent as the list `\pluginCmd{\textitcorr{standard-response}} di value bit$_1$ $\ldots$ bit$_8$' and
  the digital output is sent as the list `\pluginCmd{\textitcorr{standard-response}} do value bit$_1$ $\ldots$ bit$_8$'.
  The digital values are limited to between 0 and 255; the analog values are between zero and one.

  \pluginListCmdItem{standard-put}{bits}  
  Sets the digital output to the given value.
  The argument \objCmdArg{bits} is limited to between 0 and 255.
  Each of the digital output ports is set to the corresponding bit of the value.  

  \pluginListCmdEnd

\pluginItemComments

\pluginEnd{\pluginNameE{Phidgets}{InterfaceKit888}}

% $Log: phidg_interfacekit888.tex,v $
% Revision 1.5  2006/07/20 04:47:53  churchoflambda
% Re-added the files to record their changes.
%
% Revision 1.3  2005/08/02 15:07:09  churchoflambda
% Added CVS tags; add rail diagrams for pfsm, map1d, map2d, map3d and listen.
%
