\ProvidesFile{phidg_textlcd.tex}[v1.0.1]
\startPlugin{\pluginNameS{Phidgets}{TextLCD}}{Phidgets}{TextLCD}

\pluginItemDescription{\pluginNameD{Phidgets}{TextLCD} corresponds to the PhidgetTextLCD 20X2 device,
which displays text on an LCD screen with two rows of twenty characters.}

\pluginItemCreated{December 2003}

\pluginItemVersion{1.0.1}

\pluginItemCommands[]

  \pluginListCmdBegin

  \pluginListCmdItem{standard-do}{backlight on\textnormal{/}off}  
  Turns the LCD screen backlight on or off.

  \pluginListCmdItem{standard-do}{clear \textnormal{[}1\textnormal{/}2\textnormal{]}}  
  Clears the top row of the LCD screen (`1'), the bottom row (`2') or both rows, if no argument is given.

  \pluginListCmdItem{standard-do}{cursor left\textnormal{/}right}  
  Move the cursor of the LCD screen left or right.

  \pluginListCmdItem{standard-do}{display left\textnormal{/}right}  
  Shift the text shown on the LCD screen either left or right.

  \pluginListCmdItem{standard-do}{entrymode \textnormal{[}reverse\textnormal{]} \textnormal{[}shift\textnormal{]}}  
  Specify the text entry mode of the LCD screen.
  If `reverse' is specified, the text entry position decreases after each character is added to the screen.
  If `reverse' is not specified, the text entry position increases after each character is added to the screen.
  If `shift' is specified, the screen is shifted after each character is added to the screen,
  in the direction opposite to the text entry.
  The entered text appears to stay still while the rest of the screen moves.
  If `shift' is not specified, the screen is not shifted.

  \pluginListCmdItem{standard-do}{go row \textnormal{[}column\textnormal{]}}  
  Move the text entry point for the LCD screen to the given row (either `1' or `2') and the given column (between 1 and 20).
  If the argument \objCmdArg{column} is not present, it is assumed to be one.

  \pluginListCmdItem{standard-do}{off}
  Turn off the LCD screen.

  \pluginListCmdItem{standard-do}{on \textnormal{[}blink\textnormal{]} \textnormal{[}cursor\textnormal{]}}  
  Turn on the LCD screen.
  The cursor format is indicated by the keywords `blink' and `cursor'.
  If `blink' is specified, a block cursor will be used (the whole text cell at the cursor location will blink off and on).
  If `cursor' is specified, an underline cursor will be used.
  Both `blink' and `cursor' can be specified.

  \pluginListCmdItem{standard-do}{write anything}  
  Display the given values as text on the LCD screen.

  \pluginListCmdEnd

\pluginItemComments

\pluginEnd{\pluginNameE{Phidgets}{TextLCD}}
